VFTS682: a confirmed dynamical ejection?

### 2018-05-10 VFTS682.tex
new sec. origin

\begin{figure*}[htbp]
  \centering
  \includegraphics[width=\textwidth]{./figures/main_plot}  
  \caption{The red cross indicates the position of VFTS682. Blue stars
    are those we use to define the generic ``surroundings'', while the
    green dots indicate the stars we use to probe the core of R136,
    magnified in the inset. The red arrow shows the direction of the
    proper motion of VFTS682 relative to R136, and the gray shade
    indicates the uncertainty in the direction. \todo{orient properly, load  picture on background, add cone
      of uncertainty, maybe show pm for all stars in inset?}}
  \label{fig:main}
\end{figure*}

>>>>

The kinematic age $\tau_\mathrm{kin}$ is smaller than the apparent age
of the star age $1.0\pm 0.2$\,Myr from \cite{schneider:18}, which
corroborates the idea that the star is the result of a dynamical
ejection. The value of $\tau_\mathrm{kin}$ we find is also smaller
than the corresponding value for another massive runaway in 30 Dor,
VFTS16 for which \cite{lennon:18} inferred a kinematic age of
$\sim$1.5\,Myr. This means that the more
massive VFTS682 was ejected later than VFTS16.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{./figures/main_plot}  
  \caption{The red cross indicates the position of VFTS682. Blue stars
    are those we use to define the generic ``surroundings'', while the
    green dots indicate the stars we use to probe the core of R136,
    magnified in the inset. The red arrow shows the direction of the
    proper motion of VFTS682 relative to R136, and the gray shade
    indicates the uncertainty in the direction. \todo{load color picture on background}}
  \label{fig:main}
\end{figure}
